Optimal Fitting of Planar Curves to Prescribed Constraints

### 2014-02-13 idp/documents/documentation/paper.tex
spell checking, fixed some verbatim environments

					\begin{itemize}
						\item Any number of point, direction and curvature specifications. These \verb|CurveSpecification|s are stored in a \verb|BasicSpecification|.
						\item The curve's total length is also part of a \verb|BasicSpecification|.
						\item The curves are represented using a number of segments, each of which is represented by some function, realized using the \verb|FunctionTermCurve| class. Because of that, the number of segments as well as the function type that is used to represent each segment are part of \verb|BasicSpecification| as well. 
						The type of function used is represented using a \verb|FunctionTermCurveTemplate| object; this template allows the creation of \verb|FunctionTermCurve| objects.  
						However, this information is only used during optimization; if the number of segments and function template yield a curve with enough degrees of freedom with respect to the other specifications, roughly the same curve will be generated even if the number of segments and function template is changed. It is possible to specify the segment count and function template to modify the degrees of freedom that the resulting curves offers (i.e. more degrees of freedom mean the curve can satisfy more curve specifications while maintaining constant speed and good fairness, but the optimization process takes longer).
						\item Curves could be generated from a \verb|BasicSpecification| alone. However, if there are multiple curves that fit a \verb|BasicSpecification| very well (i.e. the optimization problem has multiple local optima), different actual curves could be generated from a \verb|BasicSpecification|. This results in a number of problems: eg., when saving a curve, if only the \verb|BasicSpecification| were saved, it would be possible that a different curve is displayed when loading the curve, because a different local optimum was reached in the optimization process. This is clearly undesirable and a way to disambiguate between the different optima is required. 
						For that reason, a full \verb|Specification| consists of a \verb|BasicSpecification| as well as some disambiguation information. That disambiguation information is the result of the optimization, which can be used as a starting position for the optimization process when a curve is loaded. This both ensures that the same curve will be generated and speeds up the optimization process as well.
					\end{itemize}

@@

					\item \verb|RootComponent| - The \verb|RootComponent| manages a list of \verb|CurveComponent|s and implements functionality to add and remove curve components. Additionally, the RootComponent implements save and load functionality.

@@

					\item \verb|FixedPositionComponent| - \verb|FixedPositionComponent|s represent the start and end of a CurveComponent.
					\item \verb|SegmentComponent| - A \verb|SegmentComponent| represents a section of a curve delimited by two PositionedControlComponents. The SegmentComponent renders the curve in that segment, but it also allows to modify the length of the curve in that segment.

>>>>

					\begin{itemize}
						\item Any number of point, direction and curvature specifications. These \verb|CurveSpecification|s are stored in a \verb|BasicSpecification|.
						\item The curve's total length is also part of a \verb|BasicSpecification|.
						\item The curves are represented using a number of segments, each of which is represented by some function, realized using the \verb|FunctionTermCurve| class. Because of that, the number of segments as well as the function type that is used to represent each segment are part of \verb|BasicSpecification| as well. 
						The type of function used is represented using a \verb|FunctionTermCurveTemplate| object; this template allows the creation of \verb|FunctionTermCurve| objects.  
						However, this information is only used during optimization; if the number of segments and function template yield a curve with enough degrees of freedom with respect to the other specifications, roughly the same curve will be generated even if the number of segments and function template is changed. It is possible to specify the segment count and function template to modify the degrees of freedom that the resulting curves offers (i.e. more degrees of freedom mean the curve can satisfy more curve specifications while maintaining constant speed and good fairness, but the optimization process takes longer).
						\item Curves could be generated from a \verb|BasicSpecification| alone. However, if there are multiple curves that fit a \verb|BasicSpecification| very well (i.e. the optimization problem has multiple local optima), different actual curves could be generated from a \verb|BasicSpecification|. This results in a number of problems: e.g., when saving a curve, if only the \verb|BasicSpecification| were saved, it would be possible that a different curve is displayed when loading the curve, because a different local optimum was reached in the optimization process. This is clearly undesirable and a way to disambiguate between the different optima is required. 
						For that reason, a full \verb|Specification| consists of a \verb|BasicSpecification| as well as some disambiguation information. That disambiguation information is the result of the optimization, which can be used as a starting position for the optimization process when a curve is loaded. This both ensures that the same curve will be generated and speeds up the optimization process as well.
					\end{itemize}

@@

					\item \verb|RootComponent| - The \verb|RootComponent| manages a list of \verb|CurveComponent|s and implements functionality to add and remove curve components. Additionally, the \verb|RootComponent| implements save and load functionality.

@@

					\item \verb|FixedPositionComponent| - \verb|FixedPositionComponent|s represent the start and end of a \verb|CurveComponent|.
					\item \verb|SegmentComponent| - A \verb|SegmentComponent| represents a section of a curve delimited by two \verb|PositionedControlComponents|. The \verb|SegmentComponent| renders the curve in that segment, but it also allows to modify the length of the curve in that segment.
